\myTitle

### 2024-08-19 tex/body-text-of-paper.tex
Add ascertainment panel sample size table to supp

We identified candidate loci with multiple single-nucleotide polymorphisms (SNPs) among multiple
populations using reduced-representation genome sequencing of 2--4 Chinook salmon, each, from a number of
populations ranging from California to British
Columbia and the interior Columbia River (\comment{Table SX}).
Genomic DNA was extracted using Qiagen DNeasy 96 Blood and Tissue Kits on a BioRobot 3000
(Qiagen, Inc). We used double-digest restriction-site associated DNA sequencing (ddRAD) with different size selections (400 bp and 500 bp
fragments) to produce a broad array of locus targets. Library preparation and sequencing methods followed those of
\citet{peterson2012double} with the modifications described in \citep{baetscher2018microhaplotypes}.
Sequencing was performed on a MiSeq (Illumina, Inc) using $2 \times 300$-cycle paired-end sequencing.

>>>>

We identified candidate loci with multiple single-nucleotide polymorphisms (SNPs) among multiple
populations using reduced-representation genome sequencing of 2--4 Chinook salmon, each, from a number of
populations ranging from California to British
Columbia and the interior Columbia River (Table~\ref{tab:ascert-panel}).
Genomic DNA was extracted using Qiagen DNeasy 96 Blood and Tissue Kits on a BioRobot 3000
(Qiagen, Inc). We used double-digest restriction-site associated DNA sequencing (ddRAD) with different size selections (400 bp and 500 bp
fragments) to produce a broad array of locus targets. Library preparation and sequencing methods followed those of
\citet{peterson2012double} with the modifications described in \citep{baetscher2018microhaplotypes}.
Sequencing was performed on a MiSeq (Illumina, Inc) using $2 \times 300$-cycle paired-end sequencing.

### 2024-08-19 tex/supplemental-tables.tex
Update major and minor Structure modes
Add ascertainment panel sample size table to supp

%%%%%%%%%%%%%%
\begin{table}
\caption{\footnotesize Allele frequencies across reporting units of the three winter-run associated
markers. Genome coordinates of SNPs are from Otsh\_v2.0. Alleles are listed according to the SNP nucleotide
at the variable SNPs within the amplicon.}
\label{tab:wrap-freqs}
{\footnotesize
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} lrrrrrrrr}
\hline\hline
Locus&Allele&CV-Winter&CV-Spring&CV-Fall&CV-Late-Fall&Cent-Cal-Coast&Klamath-Trinity&SO-NCal-Coast \\ \hline
\input{inputs/wrap-freqs.tex}
\end{tabular*}
}
\vspace*{-2.3ex}\hrule\vspace*{0.3ex}\hrule
\end{table}
%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%
\begin{table}
\caption[Microhaplotype discovery panel sample sizes]{Numbers of fish from different collections/populations used in the microhaplotype discovery effort.
$N$ is the number of diploid individuals included in the ascertainment panel.}
\label{tab:ascert-panel}
\begin{center}
{\footnotesize
\begin{tabular}{lr}
\hline\hline
Population&$N$ \\ \hline
\input{inputs/ascertainment-samples-supp-table.tex}
\\ \hline\hline
\end{tabular}
}
\end{center}
\end{table}
%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
\begin{table}
\caption[Allele frequencies of winter-run-associated polymorphisms]{Allele frequencies across reporting units of the three winter-run associated
markers. Genome coordinates of SNPs are from Otsh\_v2.0. Alleles are listed according to the SNP nucleotide
at the variable SNPs within the amplicon.}
\label{tab:wrap-freqs}
{\footnotesize
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} lrrrrrrrr}
\hline\hline
Locus&Allele&CV-Winter&CV-Spring&CV-Fall&CV-Late-Fall&Cent-Cal-Coast&Klamath-Trinity&SO-NCal-Coast \\ \hline
\input{inputs/wrap-freqs.tex}
\end{tabular*}
}
\vspace*{-2.3ex}\hrule\vspace*{0.3ex}\hrule
\end{table}
%%%%%%%%%%%%%%%
